### 2020-05-10 prep.tex
Add blank pages
Not really, LaTeX now does it for me! Because LaTeX is cool, unlike some other typesetting solution used during the compiling of these proceedings, a piece of software I am now so frustrated with that I'm fuming my frustrations in this commit message that no person should ever be reading. Seriously, are you trying to find dirt on me or something? If that's so, try reading my Twitter instead…
I think this is what Catarina meant with (chair)

\section*{Conference Organization}
	\addcontentsline{toc}{chapter}{Conference Organization}
	\subsection*{Organising committee}
	\begin{compactitem}[]
		\item[] Catarina Dutilh Novaes (Vrije Universiteit Amsterdam)
		\item[] Henrike Jansen (University of Leiden)
		\item[] Jan Albert Van Laar, chair (University of Groningen)
		\item[] Bart Verheij (University of Groningen)
	\end{compactitem}

	\subsection*{Programme committee}
	\begin{compactitem}[]
		\item[] Dale Hample, chair (University of Maryland)
		\item[] Henrike Jansen, secretary (University of Leiden)
		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
		\item[] Juho Ritola (University of Turku)
		\item[] Frank Zenker (Lund University)
 	\end{compactitem}

 	\subsection*{ECA steering committee}
 	\begin{compactitem}[]
		\item[] Lilian Bermejo Luque (University of Granada)
		\item[] Katarzyna Budzyńska (Polish Academy of Sciences)
		\item[] Henrike Jansen (University of Leiden)
		\item[] Marcin Koszowy (University of Białystok)
		\item[] Jan Albert Van Laar, deputy chair (University of Groningen)
		\item[] Marcin Lewiński (Universidade Nova de Lisboa)
		\item[] Dima Mohammed (Universidade Nova de Lisboa)
		\item[] Steve Oswald (University of Fribourg)
		\item[] Fabio Paglieri, chair (ISTC-CNR)
		\item[] Juho Ritola (University of Turku)
		\item[] Sara Rubinelli (University of Lucerne)
		\item[] Frank Zenker (University of Lund)
	\end{compactitem}

@@

>>>>

\section*{Conference Organization}
	\addcontentsline{toc}{chapter}{Conference Organization}
	\subsection*{Organising committee}
	\begin{compactitem}[]
		\item[] Catarina Dutilh Novaes (Vrije Universiteit Amsterdam)
		\item[] Henrike Jansen (University of Leiden)
		\item[] Jan Albert Van Laar (chair) (University of Groningen)
		\item[] Bart Verheij (University of Groningen)
	\end{compactitem}

	\subsection*{Programme committee}
	\begin{compactitem}[]
		\item[] Dale Hample (chair) (University of Maryland)
		\item[] Henrike Jansen (secretary) (University of Leiden)
		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
		\item[] Juho Ritola (University of Turku)
		\item[] Frank Zenker (Lund University)
 	\end{compactitem}

 	\subsection*{ECA steering committee}
 	\begin{compactitem}[]
		\item[] Lilian Bermejo Luque (University of Granada)
		\item[] Katarzyna Budzyńska (Polish Academy of Sciences)
		\item[] Henrike Jansen (University of Leiden)
		\item[] Marcin Koszowy (University of Białystok)
		\item[] Jan Albert Van Laar (deputy chair) (University of Groningen)
		\item[] Marcin Lewiński (Universidade Nova de Lisboa)
		\item[] Dima Mohammed (Universidade Nova de Lisboa)
		\item[] Steve Oswald (University of Fribourg)
		\item[] Fabio Paglieri (chair) (ISTC-CNR)
		\item[] Juho Ritola (University of Turku)
		\item[] Sara Rubinelli (University of Lucerne)
		\item[] Frank Zenker (University of Lund)
	\end{compactitem}

@@

\cleardoublepage
